---
title: R package ‘handyFunctions’ version 0.1.0
author: 
 - Copyright (C) 2022, Hongfei Liu
date: "2022/08/16"
output: github_document
theme: united
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# handyFunctions

<!-- badges: start -->

![](https://lifecycle.r-lib.org/articles/figures/lifecycle-experimental.svg) [![Codecov test coverage](https://codecov.io/gh/LuffyLouis/handyFunctions/branch/main/graph/badge.svg)](https://app.codecov.io/gh/LuffyLouis/handyFunctions?branch=main) [![R-CMD-check](https://github.com/LuffyLouis/handyFunctions/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/LuffyLouis/handyFunctions/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

The goal of handyFunctions is to get rid of the barrier to deal with non-standard data.frame format for R newbies, especially the user in bioinformatics data analysis. Besides, there are also some required plot functions for downstream analysis of dataset generated from vcftools and plink.

## Table of contents

-   [Installation](#installation)
-   [Example](#example)
    -   [ReformatDataframe](#reformatdataframe)
    -   [InteractDataframe](#interactdataframe)
    -   [Post-VCF](#post-vcf)
        -   [plotSNVdensity](#plotsnvdensity)
-   [License](#license)

## Installation {#installation}

You can install the development version of handyFunctions like so:

``` r
## Clone it from github and install it locally
git clone https://github.com/LuffyLouis/handyFunctions.git
## OR
## Install it in R
remotes::install_github("LuffyLouis/handyFunctions")
```

## Example {#example}

`handyFunctions`package contain three main sections, including ReformatDataframe, InteractDataframe, and Post-VCF. There are some basic examples which show you how to solve common problems in data analysis:

### ReformatDataframe {#reformatdataframe}

This section is designed to reformat data.frame with odd colnames, rownames, or even inappropriate dtypes for each columns.

#### unifyDataframe

Based on the following example `unifyDataframe` function, you can change the formats of raw data.frame to what you want. Especially for the dtypes in data.frame, you can set `custom=FALSE` for automatically changing into appropriate dtypes.

```{r unifyDataframe, warning=FALSE,echo=TRUE}
library(handyFunctions)
data("people")
head(people)
modifiedPeople <- unifyDataframe(people,rawColSep = '[.][.]')
head(modifiedPeople)
```

**Note**: due to the separation supporting regEx, please use the `"[.][.]"` for reformatting `people` data.frame.

### InteractDataframe {#interactdataframe}

The `InteractDataframe` section is designed for interaction between two data.frame or one data.frame and another vector.

#### mergeCustom

Sometimes, we often find it fuzzy and tedious while we'd like to merge two data.frame with different colnames. Therefore, `mergeCustom` function may be the better solution to get it rid of.

```{r mergeCustom, warning=FALSE,echo=TRUE}
library(handyFunctions)
data("people");data("grade")
head(people)
head(grade)
merged <- mergeCustom(people,grade,xcol = '..name',ycol = 'name')
head(merged)
```

### Post-VCF {#post-vcf}

#### plotSNVdensity {#plotsnvdensity}

```{r plotSNVdensity, warning=FALSE,echo=TRUE}
library(handyFunctions)
library(ggplot2)
data("SNV_1MB_density_data")
head(SNV_1MB_density_data)
ShowSNPDensityPlot(SNV_1MB_density_data,binSize=1e6,chromSet = c(38:1),withchr=T)+
  theme(axis.text.y = element_text(size=12))

```

## License {#license}

This project is published under MIT license, see file `LICENSE`.
